%-------------------------
% Resume in Latex
% Author : Vikrant Biswas
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

% Ensure that the PDF output will be all unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://windlessstorm.github.io/}{\Large Vikrant Biswas}} & Email : \href{mailto:vikrant.biswas@gmail.com}{vikrant.biswas@gmail.com}\\
  \href{http://windlessstorm.github.io/}{http://windlessstorm.github.io} & Mobile : +91-8123089095 \\
  \textsc{\small Born: \small{14-June-1992}} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {West Bengal University of Technology}{Howrah, WB, India}
      {Bachelor of Technology in Computer Science and Engineering;  CGPA: 6.45/10}{Aug. 2011 -- Sept. 2015}
    \resumeSubheading
      {Kendriya Vidyalaya}{ Barrackpore, WB, India}
      {Senior Secondary School (Class 12th);  Percentage: 73.40\%}{June. 2009 -- May. 2010}
    \resumeSubheading
      {Kendriya Vidyalaya}{ Pathankot, PB, India}
      {Secondary School (Class 10th);  Percentage: 79.80\%}{April. 2008 -- May. 2009}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mitel}{Bangalore, India}
      {Software Engineer}{Aug 2017 - Present}
    \resumeItemListStart
        \resumeItem{R\&D in cloud communications and collaboration}
            {Agile development and testing of cloud based web/mobile applications, writing E2E test and providing input on UI/UX design.}
    \resumeItemListEnd

    \resumeSubheading
      {Endurance International Group}{Bangalore, India}
      {Hosting Product Engineer}{Dec 2016 - Aug 2017}
      \resumeItemListStart
        \resumeItem{Network/System Reliability}
          {Pro-actively monitor product/services/site performance, uptime, availability and analyze logs / metrics and recommend/contribute to fixes.}
      \resumeItemListEnd

    \resumeSubheading
      {iSOKE Technologies}{Bangalore, India}
      {Software Engineer}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Userspace network processing}
          {Development of framework for fast userspace network packet processing.}
        \resumeItem{Custom packet generation}
          {Worked on the back-end appication which creates various network protocol packets and streams on-demand for various L2,L3, and L4 networking protocols.}
        \resumeItem{Quagga, Openstack}
          {Developement auto-scaling large scale network traffic simulator, ussed to simulate any kind of network topology and state.}
    
    \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Wedlay- online quiz and betting platform}
      {A online web/mobile multiplayer multiroom quiz contest platform with automated prizepool and ranking.}
    \resumeSubItem{Realtime Collaborative Whiteboard}
      {A realtime multiuser collaborative whiteboard using HTML Canvas and websockets.}
    \resumeSubItem{Home Automation}
      {IOT project with ESP8266 and Raspberry Pi for various home automation tasks.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python-4/5, JS-4/5, C-2/5, GO-2/5, RUST-2/5}
      }
    \item{
       \textbf{Framework and Technologies}{: Selenium, RobotFramework, WebdriverIO, Protractor, Jasmine, Django, NodeJS, Express, Hapi, Angular, Vue, React, Protractor, Postgres, MySQL, GCP, AWS}
     }
    \item{
       \textbf{Others}{: Git, Linux, Docker, Wireshark, KVM, VMware ESX}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------


%--------HOBBIES------------
\section{Hobbies}
  \resumeSubHeadingListStart
    \item{
      \textbf{Guitar}{: Have been trying to learn playing it since some time. Still pretty novice at it.}
      }
    \item{
       \textbf{Electronics DIY}{: Lately been learning a lot of electrical and electronics for random fun DIY projects}
     }
     \item{
      \textbf{Trekking}{: Like to go on mountain treks, have already explored most of the Western ghat treks, now want to explore northern treks}
   }
    \item{
       \textbf{Video Games}{: Love playing multiplayer competetive Video games: Dota 2, Apex Legends}
    }
    \item{
       \textbf{Reading}{: I love science fiction, current favorite is "Children of Time" by Adrian Tchaikovsky}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
