%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    { Mitel Networks Co.} % Organization
    { Project: Cloudlink Accounts Portal } % Job title
    { Software Test Developer } % Location
    { Oct. 2022 - Feb. 2023 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	 	\item { Setup automation framework in WebdriverIO in existing Angular project GIT repo for Accounts portal application, and integrated it with existing CI/CD in GitHub.
	 	}
	    \item { Fixed all existing 3 years old automated tests which were written in protractor and were in a separate automation repo, and then migrated all of them to WebdriverIO as protractor was recently announced to be deprecated and reaching End Of Life. }
        \item { Planed and wrote, developed and executed new end to end test plans for Cloudlink Accounts Portal backlog stories, as well as in sprint active stories as part of Agile development team }
        \item { Trained and onboarded team members on various topics like protractor to webdriverIO migrations, typescript, and CI/CD.
        }     
      \end{cvitems}
    }

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: MiVoice 400/2000 PBX Performance Test } % Job title
		{ Software Test Developer } % Location
		{ July. 2022 - Oct. 2022 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Investigated and evaluated various ways to performance test webRTC endpoints on Mitels PBX.
				}
				\item { Participated in discussions gathering information from the performance team on their existing tool infra, and project requirements.
				}
				\item { Build a custom scalable load test application using Puppeteer, Nodejs, and Python to generate configurable amount of webRTC traffic on Mitel PBX.
				}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel Assistant for MS Teams } % Job title
		{ Software Test Developer } % Location
		{ Aug. 2021 - July. 2022 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Setup test plan and test infrastructure for the project, after discussions with the Project manager. Which included getting new deployement environment for test, separate backend PBX instances, and new Microsoft Azure tenant and test users. } 
				\item { Setup automation test in Protractor in the Angular project GIT repo, and also connected it to Gitlab's CI/CD}
				\item { Participated in agile sprints to plan and write tests for the application features being developed in that sprint.
				}
				\item { Wrote automated tests for selected tests in Protractor in-sprint, and was able to reach 90\% code coverage.
				}
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: RayBaum Compliance and Emergency Routing Services } % Job title
		{ Software Test Developer } % Location
		{ Aug. 2020 - Aug. 2021 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Worked on testing the Common UI component being developed to be integrated accross Mitel Product for Emergency location sharing, and routing. }
				\item { Wrote automated tests in Python-selenium and Robot Framework to validated Mitel's Connect client application integration with new Common emergency call UI. And integrated test git repository with application repository.
				}
				\item { Fixed and restructured existing Python/Robot tests for Connect Client Application to work for new UI changes.
				}
				\item { Onboarded and trained new test team members on Python and Robot Framework. }
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel One Mobile } % Job title
		{ Software Test Developer } % Location
		{ Dec. 2019 - Aug. 2020 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Participated in agile sprints to test new features in Mitel's One App. }
				\item { Developed automated test for the app for both iOS, and Android versions using webdriverIO and Appium }
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel Teamwork } % Job title
		{ Associate QA Engineer Fulltime } % Location
		{ Dec. 2018 - Dec. 2019 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Participated in testing new features being developed for Mitels Teamwork Application in the current sprint, as part of agile team. }
				\item { Automated selected tests using Python, and Robot Framework. }
				\item { Setup alternative test CI/CD environment using Jenkins in parallel to existing Teamcity and custom test runner for evaluation on basis of resource consumption and ease of use. }
				\item { Investigated and implemented workarounds to do automated tests on webRTC media for Teamwork Video and audio calls in browser.
				}
				\item { Was the domain expert in the team for anything related to Python, selenium, and Robot framework. } 
				\item { Have conducted various training to upskill QA teams on automation tools and technologies like Python language, Selenium, Robot Framework }
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel Teamwork } % Job title
		{ Associate QA engineer in Contract } % Location
		{ April. 2018 - Dec. 2018 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Worked on testing the Teamwork Application and automating tests for backlog manual test cases. }
				\item { Worked on fixing various issues with the custom test runner python framework for running Python-Robot tests. 
				}
			\end{cvitems}
		}
%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel Connect Advanced Apps } % Job title
		{ Associate QA engineer in Contract } % Location
		{ Dec. 2017 - April 2018. } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Worked on planning and writing tests for new features and backlongs in various Mitels Advanced Appl projects like Mitel Telephony for Skype, and Salesforce Telephony integration. }
			\end{cvitems}
		}

%---------------------------------------------------------
	\cventry
		{ Mitel Networks Co. } % Organization
		{ Project: Mitel Connect Client } % Job title
		{ Associate QA engineer in Contract } % Location
		{ Aug. 2017 - Dec. 2017 } % Date(s)
		{
			\begin{cvitems} % Description(s) of tasks/responsibilities
				\item { Has contributed to as well as setup test automation framework for various Mitel's Connect projects which included web applications, as well as desktop Electron applications.}
				\item { The tech stack for automation was using Robot Framework, and Teamcity as well as Jenkins for CI/CD, with custom test runner in Python, which was responsible for setting up the Selenium Grid, and distributing the tests to the available agents in parallel, and then consolidating the logs. } 
			\end{cvitems}
		}

%---------------------------------------------------------
  \cventry
    { Endurance International Group } % Organization
    { Project: Bluehost }
    { Hosting Product Engineer } % Job title
    { Dec. 2016 - Aug. 2017 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Was involved in pro-actively monitoring product's, service's and site's performance and analyze metrics. Worked to resolve customer issues across the product range involving DNS, SMTP, CPANEL, and other services }
        \item { He was able to automate a lot of repetitive maintenance tasks, and common fixes, for web hosting, and backup services using Python, and bash. These scripts were then used by the entire team which greatly increased the teams efficiency. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {iSOKE Technologies } % Organization
    {Project: Aticara }
    {Software Engineer Intern} % Job title
    {May. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed application to load test network appliances with simulated traffic of various L2, L3, and L4 network protocols.}
        \item {Developed auto-scaling large-scale network traffic simulator, used to simulate multiple network topology and state.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
